### 2021-04-14 README.Rmd
added NumNe to zoneDP and plotZone and condition to the webpage.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the rundir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
rundir <- paste0(ddir,"aMSEUse/conddata/generic")  # data and results directory
dirExists(rundir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(ddir,"aMSE/data-raw/","TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"control2.csv",cleanslate = TRUE) # normally would read in a file
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,sigR=1e-08,sigB=1e-08)
# save conditioned results -----------------------------------------------------
save(zoneDD,file=filenametopath(rundir,"zoneDD.RData"))
# Illustrate productivity
propD <- getzoneprops(zoneC,zoneDD,glb,year=47)
addtable(round(t(propD),4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[45:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last three years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
cmcda <- mcdahcr(arrce=condC$histCE,hsargs=hsargs,
                 yearnames=rownames(condC$histCE),saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
#out <- prepareprojection(projC,zoneC,glb,zoneDD,ctrl,multTAC)
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            zoneDD=zoneDD,ctrl=ctrl,varyrs=6,
                            multTAC=multTAC,lastsigR = 0.25)

zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP

zoneDP <- doTASprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,mcdahcr,hsargs)
# save more plots to rundir ----------------------------------------------------
out <- plotbysau(zoneDP,glb,rundir)

projtime <- Sys.time()
print(projtime - starttime)

# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))

@@

>>>>

# LATEST UPDATE

* 2021-04-14 0.0.0.3200 Added NumNe to zoneDP output ready for its use in estimating FIS results by population and other numbers-at-size related indices. NumNe are the numbers-at-size following growth and the application of half of natural mortality but before any fishing mortality has occurred. (see News.ms for history of development)

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
rundir <- paste0(ddir,"aMSEUse/scenarios/HS652510")
datadir <- paste0(ddir,"aMSEUse/scenarios/tasdata")
alldirExists(rundir,datadir)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(rundir,"/TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"controlsau.csv",datadir=datadir,cleanslate = TRUE)
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,sigR=1e-08,sigB=1e-08)

propD <- t(getzoneprops(zoneC,zoneDD,glb,year=47))
addtable(round(propD,4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[40:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last eight years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
plotconditioning(zoneDD,glb,zoneC,condC$histCE,1973:2019,rundir)
cmcda <- mcdahcr(arrce=condC$histCE,hsargs=hsargs,
                 yearnames=rownames(condC$histCE),saunames=glb$saunames,
                 acatches=tail(condC$histCatch,1))
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            multTAC=multTAC,zoneDD=zoneDD,ctrl=ctrl,varyrs=7,
                            lastsigR = ctrl$withsigR)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

zoneDP <- doTASprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,mcdahcr,hsargs)
# save more plots to rundir ----------------------------------------------------
histCE <- condC$histCE
B0 <- getvar(zoneC,"B0")
ExB0 <- getvar(zoneC,"ExB0")
sauCI <- sauplots(zoneDP,zoneDDR,glb,rundir,B0,ExB0,startyr=25,addCI=TRUE,
                  histCE=histCE)
outzone <- poptozone(zoneDP,glb,
                     B0=sum(getvar(zoneC,"B0")),
                     ExB0=sum(getvar(zoneC,"ExB0")))
plotZone(outzone,rundir,CIprobs=c(0.05,0.5,0.95),addfile=TRUE)
projtime <- Sys.time()
print(projtime - starttime)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))

@@

After running the whole, even if you do not generate the results webpage, you could also try:

```{r }
str(zoneDP,max.level=1)

To see the structure of the dynamic object generated by the projections.
